Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-13 paper/draft1.tex
Adding more brain dumps

@@

%\renewcommand{\bibsection}{\section*{Bibliography}}
%\setlength{\bibsep}{5pt}
\bibliography{local}
\end{document}

@@

@@

more features (this is the hardest, and most manual part, may require
domain-specific knowledge, but not necessariyly, e.g. microbenchmarking)
* features derived from micro-benchmarking \citep{wong2010demystifying}
* features derived from performance limiter analysis \citep{micikevicius2010analysis}
* more instrumentation
* more data-layout
* more threading strategies to lower latency

@@

>>>>

XXX: use 300\% boost instead of 3x

@@

%\renewcommand{\bibsection}{\section*{Bibliography}}
%\setlength{\bibsep}{5pt}

@@

we believe that our approach is the most practial one to get high perf on
recent hardware, since there is no consensus on hw features (and it won't
change soon)

auto-tuning required hardward expertise *and* application-domain knowledge, we
want to remove these restrictions ultimately we want a ml-based approach to
code optimization that will where a set of generic but deep code
transformations, could be templated and injected in any domain-specific
library. this will reduce the need for specialized expertise across the range
of targetted computing systems.

@@

more features (this is the hardest, and most manual part, may require
domain-specific knowledge, but not necessariyly, e.g. microbenchmarking)
* features derived from micro-benchmarking \citep{wong2010demystifying}
* features derived from performance limiter analysis \citep{micikevicius2010analysis}
* more instrumentation
* more data-layout
* more threading strategies to lower latency
(finding a good representation is key, again...)

@@

\bibliography{local}
\end{document}
